Argennon: A Scalable Smart Contract Platform

### 2021-07-05 tex/sections/avm.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Update `README.md`
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    \texttt{methodID = (applicationID|<local prefix code>)}
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:

    \texttt{chunkID = (applicationID|accountID|<local prefix code>)}
\end{itemize}

All Argennon prefix trees have an equal branching factor \(\beta\). Therefore, we can represent an Argennon
prefix tree as a sequence of fractional numbers\footnote{It's possible to have \(a_i=0\). For
instance, \(A^{(4)}=(0.2000)_{10}\) is a valid prefix tree.} in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)
\]
Where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)}<A^{(i+1)}\). A typical choice for \(\beta\)
could be \(2^8\).

@@

In Argennon, the root smart contract is an updatable smart contract, which can be updated by the Argennon consensus
protocol. This means that bugs or security vulnerabilities in the AVM standard library could be quickly patched and
smart contracts can use the AVM standard library safely. Many important and useful functionalities,
such as fungible and non-fungible assets, access control mechanisms,
and general purpose DAOs are implemented in the Argennon standard library.

>>>>

    \texttt{methodID = (applicationID|<local-prefix-code>)}
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:

    \texttt{chunkID = (applicationID|accountID|<local-prefix-code>)}
\end{itemize}

All Argennon prefix trees have an equal branching factor \(\beta\). Therefore, we can represent an Argennon
prefix tree as a sequence of fractional numbers\footnote{It's possible to have \(a_i=0\). For
exmaple \(A^{(4)}=(0.2000)_{10}\) is correct.} in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)\ ,
\]
where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)}<A^{(i+1)}\). A typical choice for \(\beta\)
could be \(2^8\).

@@

In Argennon, the root smart contract is an updatable smart contract, which can be updated by the Argennon consensus
protocol. This means that bugs or security vulnerabilities in the AVM standard library could be quickly patched and
smart contracts could benefit from bugfixes and improvements of the AVM standard library even if they are
non-updatable. Many important and useful functionalities,
such as fungible and non-fungible assets, access control mechanisms,
and general purpose DAOs are implemented in the Argennon standard library.
